Exp. 2 Analysis: 2AFC, adults vs. children

### 2021-01-15 analysis/exp2_analysis.Rmd
new mturk data

```{r load-human-data, echo=FALSE}
raw = read_csv("exp2-mturk-data/MturkAdultDrop-Data-Combined.csv")
# row 1 is empty, row 2 should be header
d = raw[3:nrow(raw),]
names(d) = raw[1,]
d[,"NA"] = NULL
names(d) <- make.unique(names(d))
d[which(is.na(d$Exclude)),]$Exclude = 'N'

@@

# Q38-Q41 = which toy did you just drop? (catch trials)
d = d %>% 
  dplyr::select(-Q11, -Q38, -Q39, -Q40, -Q41, -Q42, -Q43, -`Random ID`) %>%
  rename(Duration = `Duration (in seconds)`)
#write.csv(d, file="exp2_cleaned.csv")

>>>>

```{r load-human-data, echo=FALSE}
#raw_old = read_csv("exp2-mturk-data/MturkAdultDrop-Data-Combined.csv")
raw = read_csv("exp2-mturk-data/MturkAdultDrop DataRound2  - Combined.csv")
# row 1 is empty, row 2 should be header
d = raw[3:nrow(raw),]
names(d) = raw[1,]
d[,"NA"] = NULL
names(d) <- make.unique(names(d))
d[which(is.na(d$Exclude)),]$Exclude = 'N'

@@

# Q38-Q41 = which toy did you just drop? (catch trials)
d = d %>% # Q38 no longer exists ..
  dplyr::select(-Q11,  -Q39, -Q40, -Q41, -Q42, -Q43, -`Random ID`) %>% # -Q38,
  rename(Duration = `Duration (in seconds)`)
#write.csv(d, file="exp2_cleaned.csv")
